### 2017-06-20 manuscript/usses_water_ms.Rmd
updates figures; caches some stuff

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{../figures/glmm_treatment_posteriors.png}
  \caption{Posterior distributions of treatment-level parameters ('Intercept' and the effect of 'Precipitation') from the ANPP-Precipitation model.}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{../figures/glmm_yeardiffs.png}
  \caption{Posterior distributions of yearly treatment effects from the ANPP-Treatment model.}
\end{figure}

>>>>

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{../figures/glmm_treatment_posteriors.png}
  \caption{Posterior distributions of treatment-level parameters ('Intercept' and the effect of 'Soil Moisture'). Kernel bandwidths of posterior densities were adjusted by a factor of 5 for visual clarity.}
\end{figure}

<!---
\newpage{}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{../figures/glmm_yeardiffs.png}
  \caption{Posterior distributions of yearly treatment effects from the ANPP-Treatment model.}
\end{figure}\
--->
